---
title: "Lab Work 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("~/Google Drive/Documents/PHD documents/Classes/Advanced Bioinformatics/Lab2/lab2data")
```

#1)How do you ask if a file exists?

```{r}
file.exists('data')
```

#2)How to you ask if a file is a directory?
```{r}
file_test("-d", 'data')
```

#3)How do you remove (delete) a file?
```{r}
file.remove('test')
```

#4)How do you get the size of a file?
```{r}
file.info('data')
```

#5)How do you get all the file names matching a pattern?
```{r}
list.files(path="data/", pattern= 'txt')
```

#6)How do you get all the file names matching a pattern recursively?
```{r}
list.files(pattern = "*", recursive = TRUE)
```

#8)How do you open gzip-compressed files for reading and for writing?
```{r}
file <- read.csv(zip.file.extract(file, zipname="R.zip")
```

#Checking which files are missing:

#Create a list of files:
```{r}
a <- list.files(path="data/", pattern= 'a.txt')
b <- list.files(path="data/", pattern= 'b.txt')
output = list.files(path="output/", pattern= '*')

```

#Create a theoretical list of output files that are supposed to be present:
```{r}
result <- list()
for (i in 1:length(a))
{result[i] <- paste('outfile.',i,'.a.out',sep='')}
for (i in 1:length(b))
{result[50+i] <- paste('outfile.',i,'.b.out',sep='')}
```

#Compare and print the output files that are missing from the theoretical list:
```{r}
result[!(result %in% output)]
```

